Scaffolder - Software for Manual Genome Scaffolding.

### 2011-09-12 src/article.tex
Spell check

A use case for Scaffolder is a combination of computational and manual editing
of a genome scaffold. We have used Scaffolder in our own genome projects to
create an initial scaffold from compuationally parsing the output of \emph{in
silico} scaffolding tools into YAML. This scaffold was then manually updated as
the scaffold was finished with additional gap-filling sequences generated in
the laboratory. This is example of the scaffolder format being both
compuationally tractable while being simple to edit manually. \pb

>>>>

A use case for Scaffolder is a combination of computational and manual editing
of a genome scaffold. We have used Scaffolder in our own genome projects to
create an initial scaffold from computationally parsing the output of \emph{in
silico} scaffolding tools into YAML. This scaffold was then manually updated as
the scaffold was finished with additional gap-filling sequences generated in
the laboratory. This is example of the scaffolder format being both
computationally tractable while being simple to edit manually. \pb
